---
title: "Tutorial"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)

recorder <- function(tutorial_id, tutorial_version, user_id, event, data){
  timestamp = Sys.time()
  
  data$tutorial_id = tutorial_id
  data$tutorial_version = tutorial_version
  data$user_id = user_id
  data$timestamp = timestamp
  
  saveRDS(data, paste(format(timestamp, "%Y_%m_%d_%H_%M_%OS2"), "-", event, ".rds", sep="") )
  }

options(tutorial.event_recorder = recorder)

```

## Topic 1

### Exercise 

*Here's a simple exercise with an empty code chunk provided for entering the answer.*

Write the R code required to add two plus two:

```{r two-plus-two, exercise=TRUE}

```

### Exercise with Code

*Here's an exercise with some prepopulated code as well as `exercise.lines = 5` to provide a bit more initial room to work.*

Now write a function that adds any two numbers and then call it:

```{r add-function, exercise=TRUE, exercise.lines = 5}
add <- function() {
  
}
```

## Topic 2

### Exercise with Hint

*Here's an exercise where the chunk is pre-evaulated via the `exercise.eval` option (so the user can see the default output we'd like them to customize). We also add a "hint" to the correct solution via the chunk immediate below labeled `print-limit-hint`.*

Modify the following code to limit the number of rows printed to 5:

```{r print-limit, exercise=TRUE, exercise.eval=TRUE}
mtcars
```

```{r print-limit-hint}
head(mtcars)
```

### Quiz

*You can include any number of single or multiple choice questions as a quiz. Use the `question` function to define a question and the `quiz` function for grouping multiple questions together.*

Some questions to verify that you understand the purposes of various base and recommended R packages:

```{r quiz}
quiz(
  question("Which package contains functions for installing other R packages?",
    answer("base"),
    answer("tools"),
    answer("utils", correct = TRUE),
    answer("codetools")
  ),
  question("Which of the R packages listed below are used to create plots?",
    answer("lattice", correct = TRUE),
    answer("tools"),
    answer("stats"),
    answer("grid", correct = TRUE)
  )
)
```

```{r}
verbatimTextOutput("view-session", placeholder = FALSE)
verbatimTextOutput("view-detail", placeholder = FALSE)
verbatimTextOutput("container-files", placeholder = FALSE)
verbatimTextOutput("user-files", placeholder = FALSE)
```

```{r context="server"}
output$`view-session` <- renderPrint(session)
output$`view-detail` <- renderPrint(session$user)
#output$`view-detail` <- renderPrint(rlang::env_print(session$userData))
#output$`view-detail` <- renderPrint(session$userData$learnr_state)
output$`view-detail` <- renderPrint(system("whoami", intern=TRUE))
output$`container-files` <- renderPrint(list.files())
output$`user-files` <- renderPrint(list.files("~/workspace/Storage/klovett2/persistent/katie-test"))

```

```{r context="server"}
KATIE_STORAGE = "~/workspace/Storage/klovett2/katie-test/"

export_events <- function(event_location = ".", event_destination = KATIE_STORAGE) {
  # print("session end")
  # list.files(event_location)
  # list.files(KATIE_STORAGE)
  file.copy(list.files(event_location), KATIE_STORAGE)
}

onSessionEnded(export_events, session = getDefaultReactiveDomain())
```
